---
title: "Fortnite X Travis Scott - World's first in-game concert"
output: html_document
---

```{r setup, include=FALSE}
 knitr::opts_chunk$set(message = FALSE, warning = FALSE) 
                     # message = FALSE, echo = TRUE, dpi = 180,
                    #  fig.width = 8, fig.height = 5)

library(data.table)
library(ggplot2)
library(tidyverse)
library(forcats)

# read full data set
dt <- fread('../../gen/analysis/temp/preclean.csv')

# load the different data sets 
Before <- fread("../../gen/analysis/temp/preclean-before.csv") %>% as_tibble() %>% 
  # met mutate voeg je een kolom toe, waarde voor kolom moment = voor 
    mutate(moment = "Before")

During <- fread("../../gen/analysis/temp/preclean-during.csv") %>% as_tibble() %>% 
  mutate(moment = "During")

After <- fread("../../gen/analysis/temp/preclean-after.csv") %>% as_tibble() %>% 
    mutate(moment = "After")

```

Buckle your seatbelts, because in seven small graphs, and brief statistic summeries, we are going to learn you something about the wonders of the first-ever in-game concert by the one and only rap hero: Travis Scott. So sit down, relax, and enjoy the experience of our many-hours-struggling-to-program-extravaganza.


### Plots 

Below you find the plots on the polarity scores 'before', 'during' and 'after' the event. Positive perceivement is split from negative perceivement to be able to see a clear distinction. 

```{r, echo = FALSE}
# read final data
# Merge data
# Start with "Before" 
Dataset <- Before %>% 
  # 'Bind rows' to add rows. Only possible when all columns are equal, therefore, we called every column 'moment'
  bind_rows(During) %>% 
  bind_rows(After) %>% 
  # 'mutate' creates another new column
  # 'case when' is a if_else function, but for multiple conditions
  mutate(Eigen_polarity = case_when(
    polarity > 0 ~   "Positive",
    polarity < 0 ~  "Negative",
    #?case_when
    # Should end with TRUE ~value, this is a function of 'case_when'
    TRUE ~ "Neutral"
  ))

Dataset %>% 
  # Over here we relevel the variable 'moment',
  # this becomes possible when we made 'moment' into a factor
  # str(Dataset$mutate) # factor
  # fct_relevel = factor_relevel
  mutate(moment = moment %>% as_factor(),
         moment = moment %>% fct_relevel("Before", "During", "After")) %>% 
  
  # Remove Neutral plot 
  filter(Eigen_polarity != "Neutral") %>% 
  # ggplot is the functie to make a plot
  # x = polarity, no y variables because geom_histogram does this itself (counts rows)
  ggplot(aes(x = polarity, fill = moment)) +
  # number of bins = 10, eventually adjust. Default = 30
  geom_histogram(bins = 10) +
  # scales = free makes sure the x-as en y-as are scaled freely 
  # free_x scales all y-as equal
  facet_wrap(Eigen_polarity ~ moment, scales = "free_x")
```

### Summary statistics

```{r}
summary(Before)
summary(During)
summary(After)
```

### Plots full dataset
```{r, echo = FALSE}
# Creates histogram for overview
ggplot(dt, aes(x=polarity)) +
  geom_histogram(fill="blue", alpha=0.5, position="identity") + ggtitle('Polarity distribution')
```

### Summary statistics full dataset

```{r, echo= FALSE}
summary(dt)
```

### Distribution polarity x time sets

```{r, echo = FALSE}
Dataset %>% 
  mutate(moment = moment %>% as_factor(),
         moment = moment %>% fct_relevel("Before", "During", "After")) %>% 
  group_by(moment) %>% 
  count(Eigen_polarity) %>% 
  mutate(pct = n / sum(n),
         Percentage = scales::percent(pct)) %>% 
  select(-pct) %>% 
  DT::datatable()
  
```

For more information or questions about the analysis please refer to m.terweij@tilburguniversity.edu
